### 2019-02-18 sections/intuition.tex
wording
Tasks can share information

In a step $t \Next e$, the decision to move on to e is taken by $\Next$, not by t.
The decision is based on a speculative evaluation of $e$.
The step combinators in $t \Then e$ and $t \Next e$ pass the value $v$ of $t$ to the continuation $e$.
Both steps act like $t$ as long as the step is guarded.
A step is guarded as long as the speculative evaluation $e\ v$ yields $\Fail$.
Once it becomes unguarded, the task continues as $e\ v$.
The task $t \Next e$ requires a continue event $\Continue$ in addition to the step being unguarded.
We designed speculative evaluation so that it does not have side effects.

@@

We have already seen communication between tasks by means of the step
combinator. The resulting value from the left task is passed on to the task on
the right. The second method of internal communication between tasks is shared
data.
Shared data represents data flow \emph{across} control flow.
Shared data sources are assignable references, whose changes in value are immediately visible to all tasks interested in them.
The semantics of \TOPHAT requires all updates to shared data and all enabled internal steps to be processed before any further communication with the environment can take place.

>>>>

In a step $t \Next e$, the decision to move on to e is taken by $\Next$, not by t.
The decision is based on a speculative evaluation of $e$.
The step combinators in $t \Then e$ and $t \Next e$ pass the value $v$ of $t$ to the continuation $e$.
Both steps act like $t$ as long as the step is guarded.
A step is guarded as long as the speculative evaluation $e\ v$ yields $\Fail$.
Once it becomes unguarded, the task continues as $e\ v$.
The task $t \Next e$ requires a continue event $\Continue$ in addition to the step being unguarded.
Speculative evaluation is designed so that it does not have side effects.

@@

The step combinator is one form of internal communication, where task values are passed to continuations.
Another form of internal communication is shared data.
Shared data enables data flow \emph{across} control flow, in particular between parallel tasks.
Shared data sources are assignable references whose changes are immediately visible to all tasks interested in them.
The semantics of \TOPHAT requires all updates to shared data and all enabled internal steps to be processed before any further communication with the environment can take place.
